Naturalness in U(1) extensions of the MSSM

### 2015-01-23 paper/e6ssm-tuning-paper.tex
Filled in more precise values of minimum tunings in the conclusion

In contrast we find that in $U(1)$ extensions of the MSSM there is an
additional way to constrain the naturalness of the models, which is
through the $Z^\prime$ mass limit.  We find when we impose a low
cutoff of $20$ TeV for setting the soft masses, the lowest tuning in
the E$_6$SSM is compatible with a $Z^\prime$ mass of $2.5$ TeV was
$\Delta \approx 100$, while if the LHC run II can place a limit of
$4.5$ TeV on $M_Z^\prime$ then the tuning would be just under $400$.
By comparison the current situation in the MSSM only requires a tuning
of around $20-30$. [Dylan: update numbers a bit -- I suck at reading
  them off the graphs:)] This should be interpreted as saying that in
the most conservative limits one can place on naturalness on these
models, the tuning in the E$_6$SSM is worse.  However if there are no
charginos below $700$ GeV then the situation in the two models would
be the same.

>>>>

% DH:: I've given the minimum overall tunings for each, would it be
% better to give the minimum for a 125 GeV Higgs (which is
% ~38 for the MSSM, at a Higgs mass of 125.04 GeV, \tan\beta = 50,
% vs. ~122 for a 2.5 TeV Z' and 393 for a 4.5 TeV Z' with m_h = 125.5 GeV
% (this increases to ~416 for a 125 GeV Higgs exactly)
In contrast we find that in $U(1)$ extensions of the MSSM there is an
additional way to constrain the naturalness of the models, which is
through the $Z^\prime$ mass limit.  We find when we impose a low
cutoff of $20$ TeV for setting the soft masses, the lowest tuning in
the E$_6$SSM is compatible with a $Z^\prime$ mass of $2.5$ TeV was
$\Delta \approx 112$, while if the LHC run II can place a limit of
$4.5$ TeV on $M_Z^\prime$ then the tuning would be approximately $380$.
By comparison the current situation in the MSSM only requires a tuning
of around $33$. This should be interpreted as saying that in
the most conservative limits one can place on naturalness on these
models, the tuning in the E$_6$SSM is worse.  However if there are no
charginos below $700$ GeV then the situation in the two models would
be the same.
